Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-14 paper/sec-mva.tex
updated mva section

We can finally combine the three categories, resolved,
intermediate and boosted, and determine the overall signal
significance, finding
\be
\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 4.0 \, ,\quad
\mathcal{L}=3\,{\rm ab}^{-1}\, .
\ee
%
We thus conclude that the measurement of
Higgs pair production in the $b\bar{b}b\bar{b}$ final state
should be 
well above the threshold for evidence.
%
Even
discovery might be within reach if the
misidentification of light and charm jets as b-jets can be  reduced.
%
Extrapolating the above results
to total integrated luminosity expected at the end of
LHC Run II, one finds
instead
\be
\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 1.3(2.6) \, ,\quad
\mathcal{L}=300\,{\rm fb}^{-1}\, ,
\ee
where the number in brackets corresponds to neglecting all backgrounds
except for the QCD $4b$ multijets.
%
This suggest that, remarkably, accessing Higgs pair production at Run II
might not be completely impossible, specially accounting
for the fact that the mean number of PU events per
bunch crossing is much smaller
that at the HL-LHC.

>>>>

Combining the three categories, resolved,
intermediate and boosted, we determine the overall signal
significance, finding
\be
\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 4.0~(1.3) \, ,\quad
\mathcal{L}=3000~(300)\,{\rm fb}^{-1}\, .
\ee
%
We thus conclude that the measurement of
Higgs pair production in the $b\bar{b}b\bar{b}$ final state at the HL-LHC
should be 
well above the threshold for evidence.
%
On the other hand, such measurement seems to be out of reach
for the total integrated luminosity expected by the end of Run II.

In Table~\ref{table:cutflowMVA_fakes} we compare,
after the MVA is applied,
the total
number of background events, $N_{\rm ev}^{\rm tot}$,
    expected at the HL-LHC, with
     $N_{\rm ev}^{\rm 4b}$, the corresponding number
    from the QCD $4b$ component, in the cases with and without
    PU.
    %
    The MVA has been trained to the total background sample,
    though differences
    in the kinematic distributions of the $4b$ and $2b2j$ processes are small,
    see Fig.~\ref{fig:histoBack}.
    %
    The major improvement of eliminating the contamination
    of light and charm jet mis-identification is in the boosted category.

    In the case of PU+SK, combining the three categories but assuming that
    the only relevant background is the irreducible QCD $4b$ component,
    we obtain
    \be
\lp \frac{S}{\sqrt{B_{\rm 4b}}}\rp_{\rm tot} \simeq 7.4(2.4) \, ,\quad
\mathcal{L}=3000 (300)\,{\rm fb}^{-1}\, ,
\ee
Therefore, a discovery of Higgs pair production at the
HL-LHC might be possible if the
mis-identification of light and charm jets as
$b$-jets can be  reduced.
%
With these assumptions, and provided
the signal efficiency can be further enhanced,
this measurement might even be feasible
by the end of Run II.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \centering
  \small
  \begin{tabular}{|c|c|c|c||c|c||c|c|}
        \hline
        Category  &    &  $N_{\rm ev}^{\rm tot}$  &  $N_{\rm ev}^{\rm 4b}$   &
        $S/\sqrt{B_{\rm tot}}$ & $S/\sqrt{B_{\rm 4b}}$  
        &  $S/B_{\rm tot}$ & $S/B_{\rm 4b}$\\ 
    \hline
    \hline
    \multirow{2}{*}{Boosted} &  no PU  & $2.2\cdot 10^4$  & 4800    & 
      5.4 &  11.6 & 0.034 & 0.16 \\
    & PU+SK & 7300  &  1600  &  2.9  & 6.2 &  0.034 & 0.16 \\
    \hline
    \hline
    \multirow{2}{*}{Intermediate} &  no PU   & $5.5\cdot 10^3$  & 2000    &
    4.8  &  7.9 &  0.06  &  0.16 \\
    & PU+SK  & 2600   &  1000  & 1.1  & 1.8 & 0.02 & 0.05 \\
    \hline
    \hline
    \multirow{2}{*}{Resolved} &   no PU  & $8\cdot 10^4$   &
    $3.7\cdot 10^4$
    & 4.5  & 6.7  & 0.01 & 0.02 \\
    & PU+SK  &  $3\cdot 10^4$   &   $1.3\cdot 10^4$ & 2.5    & 3.7  & 0.015 & 0.03 \\
    \hline
      \end{tabular}
  \caption{\small Post-MVA number of total background events, $N_{\rm ev}^{\rm tot}$,
    expected at the HL-LHC, compared
    with $N_{\rm ev}^{\rm 4b}$,
    the number of QCD $4b$ background events.
    %
    We also indicate the corresponding signal significance and signal over background
    ratios.
        \label{table:cutflowMVA_fakes}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
